### 2018-10-24 pkg/model4you/inst/JORS/man_model4you.Rnw
revision JORS
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2362 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 5edb103fec7acbeff2896ea7d7abcb248dff1aa9

A tree based on this model can be computed and visualised in only two lines of
code:
<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for the Mathematics Exam datam.">>=
tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2))
plot(tr_math, terminal_panel = node_pmterminal(tr_math,
                                               plotfun = lm_plot))
@
\new{
We restrict the depth of the tree to two (\Sexpr{'maxdepth = 2'}) for
illustration purposes. If this setting is not used a more complex tree would
be estimated.
}
The tree (see Figure~\ref{fig:math_tree}) divides students based on the
percentage of successful online \Sexpr{'tests'}. These online tests were
conducted biweekly throughout the semester.  The largest difference between the
two exam groups is in the students who did very well in the online tests (more
than \Sexpr{round(tr_math[[5]]$node$split$breaks, 1)} percent correct). The
tree thus gives us much more information on the fairness of the exam than the
simple linear model, which is that it does not seem to be fair for students who
did very well throughout the semester (at this point we should state that the
students self selected into the two exam groups which might also be the reason
for differences in exam performance).
\new{Note that confidence intervals shown in the tree are not adjusted and should
hence be interpreted as a measure for variablity and not be used for inference.}

>>>>

A tree based on this model can be computed and visualised in only two lines of
code:
<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for the Mathematics Exam datam.">>=
tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2))
plot(tr_math, terminal_panel = node_pmterminal(tr_math,
                                               plotfun = lm_plot))
@
\new{
We restrict the depth of the tree to two (\Sexpr{'maxdepth = 2'}) for
illustration purposes. If this setting is not used a more complex tree would be
estimated. Also the cutpoints and effect estimates are rounded in the plot.  To
view the tree in the R console, the command \Sexpr{'print()'} function can be
used.
}
<<math_printtree>>=
print(tr_math)
@
The tree (see Figure~\ref{fig:math_tree}) divides students based on the
percentage of successful online \Sexpr{'tests'}. These online tests were
conducted biweekly throughout the semester.  The largest difference between the
two exam groups is in the students who did very well in the online tests (more
than \Sexpr{round(tr_math[[5]]$node$split$breaks, 1)} percent correct). The
tree thus gives us much more information on the fairness of the exam than the
simple linear model, which is that it does not seem to be fair for students who
did very well throughout the semester (at this point we should state that the
students self selected into the two exam groups which might also be the reason
for differences in exam performance).
\new{Note that confidence intervals shown in the tree are not adjusted and
should hence be interpreted as a measure for variablity and not be used for
inference.}
